\documentclass[11pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=.5in]{geometry}
\setlength{\parindent}{0ex}

\begin{document}
\pagenumbering{gobble} % remove page numbers

\begin{center}
		\begin{tabular}{c}
			\begin{LARGE}
				\href{https://www.linkedin.com/in/kieran-warwick}{Kieran Warwick}
			\end{LARGE}
			\\
				\href{mailto:kieran.warwick@bath.edu}{kieran.warwick@bath.edu}
				$\vert$
				\href{https://github.com/kw510}{GitHub @ kw510}
			\\
				London, UK  
	\end{tabular}
\end{center}

\vfill

Software Engineer at Thirdfort, Master Computer Science Graduate from the University of Bath, with First Class Honours.  
Open to new and interesting challenges, with opportunities for fast growth and self-development. Enjoys contributing to 
real world problems, making the world better and more secure!

\section*{\normalfont Relevant Experience}
	\subsection*{
			Software Engineer
			\hspace{0.59in}\hfill\normalfont Thirdfort 
			\hfill\normalfont\emph{ Nov. 2020 - Present }
		}

		\begin{itemize}
			\item Developed a new security component and lead migration of existing records, 
						achieving a zero downtime launch with over 32 million records migrated. 
						It allows us the scale the system, improving GET requests ~47\%, to an average of 50ms.
			\item Lead a small team and developed a new billing component; Trained successor to take over component.
						Included transitioning Node to Go, Kafka to PubSub, http to gRPC, Kubernetes to Google Cloud Run.
			\item Coached and mentored joiners and members of the team, generally contributing to technical discussions.
			\item Helping with DevOps responsibilities including:
						Deploying Pods and Services to the Kubernetes cluster and
						managing PubSub topics + subscriptions. Also finding and solving ongoing production issues.
			\item Worked with the product, operations, design and support teams, helping deliver technical knowledge.
		\end{itemize}

	\subsection*{
			Taught Academic Representative
			\hfill\normalfont Bath University
			\hfill\normalfont\emph{ Oct. 2017 - June 2018 }
		}

		\begin{itemize}
			\item Gathered and represented students' opinions of the course upon Staff Student Liaison Committees,
						acting as a bridge of communication between students and the SU
		\end{itemize}

	\subsection*{
			Academic Peer Mentor
			\hspace{0.8in}\hfill\normalfont Bath University 
			\hfill\normalfont\emph{ Oct. 2017 - June 2018 }
		}

		\begin{itemize}
			\item Mentored a small group of first year students, helping them with their studies and adjusting to university.
		\end{itemize}

\hrule\vspace{0.175in}

\begin{minipage}{0.475\textwidth}
	\section*{\normalfont Education}
		\vfill\subsubsection*{University of Bath\hfill \normalfont\textit{2016-20}}\vspace{-0.25cm}
		Master of Computer Science $\vert$ \textbf{First Class Honours}

		\vfill\subsubsection*{Chichester High Schools' Sixth Form \hfill \normalfont\textit{2013-16}}\vspace{-0.25cm}
		A-levels: Maths: \textit{A*},  Further Maths: \textit{A}, Physics \textit{A}
		
		\vfill\subsubsection*{Chichester High School for Boys\hfill \normalfont\textit{2011-13}}\vspace{-0.25cm}
		GCSEs: \textit{6As, 3Bs, 3Cs} - including Maths \& English

	\section*{\normalfont Academic Projects}
		\vfill\subsubsection*{Serious Game: Turing Machine Diagrams}
			Web application teaching Turing machines through the use of state-transition diagrams.
			Deployed at: \url{https://interactive-turing.herokuapp.com}
		
		\vfill\subsubsection*{Analysis of Extended-Precision upon GPUs}
			Uses two floats to estimate a double, with arithmetic. Provides a speedup of up to 1.2 on consumer GPUs. 
			Available at: \url{https://github.com/kw510/DFGPU}

\end{minipage}
\hfill
\begin{minipage}{0.475\textwidth}
  % Get though skill buzzword filters
	\section*{\normalfont Areas of Knowledge}
		Machine Learning;
		Data Science;
		Cyber Security;
		Artificial Intelligence;
		Databases;
		Entrepreneurship;
		Parallel Computing;
		Networking;
		Safety-Critical Systems;
		Control and Cognitive Systems;
		Computer Architecture;
		Functional Programming;
		Algorithms and Data Structures;
		Visual Computing;
		Interactive Systems;
		Principles of Programming Languages;
		Full Stack Web Development.
		
	\vspace{-0.9mm}

  % Get though frameworks/languages buzzword filters
	\section*{\normalfont Technologies}
		GoLang,
		JavaScript,
		Python,
		gRPC,
		Java,
		C,
		MATLAB,
		Node.JS,
		MongoDB,
		React,
		Haskell,
		OpenMP,
		MPI,
		SQL,
		NoSQL,
		PHP,
		HTML5,
		CSS,
		\LaTeX,
		Windows,
		MacOS,
		Linux.
	\section*{\normalfont Awards \& Interests}
	Winner of design competition for Ergo Computing.

	Attending Hackathons with a small team.

	Cyclist, going out with local cycling clubs.

	Coffee enthusiast, with a AeroPress + hand grinder.
\end{minipage}
\vfill
\emph{References available on request}

\end{document}